---
title: "Templates"
output: 
  html_document: 
    keep_md: yes
---

Thank you for contributing to Fun<sup>fun</sup> (a fungal functional trait database). Below you will find a set of templates for the essential files used to generate the dataset.

# Data file template


```{r, echo=FALSE}
library(knitr)
dat <- read.csv("data.csv")

kable(dat[1:5,])
```

```{r, echo=FALSE}
library(magrittr)
readLines("data.csv") %>% 
  paste0(collapse="\n") %>% 
  openssl::base64_encode() -> encoded
```


[Download the template for data.csv](`r sprintf('data:text/csv;base64,%s', encoded)`) **or** open it directly in your  <a download="dataMatchColumns.csv" href="`r sprintf('data:application/csv;base64,%s', encoded)`">browser</a>



# Template for dataMatchColumns.csv


```{r, echo=FALSE}
library(knitr)
dat <- read.csv("dataMatchColumns.csv")

kable(dat)
```

```{r, echo=FALSE}
library(magrittr)
readLines("dataMatchColumns.csv") %>% 
  paste0(collapse="\n") %>% 
  openssl::base64_encode() -> encoded
```

[Download the template for dataMatchColumns.csv](`r sprintf('data:text/csv;base64,%s', encoded)`) **or** open it directly in your  <a download="dataMatchColumns.csv" href="`r sprintf('data:application/csv;base64,%s', encoded)`">browser</a>



# Template for study metadata


```{r, echo=FALSE}
library(knitr)
dat <- read.csv("studyMetadata.csv")

kable(dat)
```

```{r, echo=FALSE}
library(magrittr)
readLines("studyMetadata.csv") %>% 
  paste0(collapse="\n") %>% 
  openssl::base64_encode() -> encoded
```

[Download the template for studyMetadata.csv](`r sprintf('data:text/csv;base64,%s', encoded)`) **or** open it directly in your  <a download="dataMatchColumns.csv" href="`r sprintf('data:application/csv;base64,%s', encoded)`">browser</a>



# Template for .bib file for study reference


@article{wallace1902island,


  title={Island life, or, the phenomena and causes of insular faunas and floras: including a revision and attempted solution of the problem of geological climates},
  
  
  author={Wallace, Alfred Russel},
  
  
  journal={Journal of Biogegraphy},
  
  
  volume={58},
  
  
  number={1},
  
  
  pages={19-20},
  
  
  year={2008},
  
  
  publisher={Macmillan}
}


```{r, echo=FALSE}
library(magrittr)
readLines("studyRef.bib") %>% 
  paste0(collapse="\n") %>% 
  openssl::base64_encode() -> encoded
```

[Download the template for the study reference](`r sprintf('data:text/csv;base64,%s', encoded)`) **or** open it directly in your  <a download="dataMatchColumns.csv" href="`r sprintf('data:application/csv;base64,%s', encoded)`">browser</a>



# Template for study contact information


```{r, echo=FALSE}
library(knitr)
dat <- read.csv("studyContact.csv")

kable(dat)
```

```{r, echo=FALSE}
library(magrittr)
readLines("studyContact.csv") %>% 
  paste0(collapse="\n") %>% 
  openssl::base64_encode() -> encoded
```


[Download the template for study contact information](`r sprintf('data:text/csv;base64,%s', encoded)`) **or** open it directly in your  <a download="dataMatchColumns.csv" href="`r sprintf('data:application/csv;base64,%s', encoded)`">browser</a>
  